BurgerMax Presents: Open Adcess

### 2017-03-01 future-work.tex
Conclusion and future work fill ins

\subsection{Subvert Academic Thought}
\todo{Pivot academic thought away from mathematical and computational problems.
Wasted  brainpower when they could be thinking about products and brands.}

\subsection{ACM Seizes Means of Production}
\todo{By putting crushed crystals in CEO's coffee, the ACM will influence CEOs
  to liquidate their companies and give them to the ACM.
  The mills were originally for crushing crystals but after the revolution they
were re purposed to generate electricity
ESPN executives are Mormon though and impervious to crystal healing and coffee. So we had to compromise: the entire National Park System became an ESPN Zone.
}

@@

\todo{Servers powered by manual labor (guy in basement pushing bar around).  If
you want an ad free version you can visit your local ACM work dungeon to
manually turn a generator.)}

\todo{Set system clock to run 10 to the 8 times slower than real time for
reporting performance numbers as recommended by
https://queue.acm.org/detail.cfm?id=3036398}

>>>>

\subsection{Subvert Academic Thought}
Our native advertising proposal contained within the revolutionary Open Adcess
\cite{this} paper was much more effective than we ever could have imagined at
the time.
Rather than simply increasing brand awareness, we were able to transform
academic thinking away from mathematical and computational problems and
instead onto products and brands.
Computer scientists today have solved the worlds biggest problems in branding
and marketing while believing they were wasting all that brainpower on math.

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production.
The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder.
This powder was slipped into the coffee of unsuspecting CEOs where it worked to
slowly make them more acceptable to the messages of the ACM.
After years of crystal ingestion, the CEOs of the world's largest companies
ceded control of their companies to the ACM.
We are happy to announce that there currently exist no companies other than the
ACM.

@@

%Set system clock to run 10 to the 8 times slower than real time for
%reporting performance numbers as recommended by
%https://queue.acm.org/detail.cfm?id=3036398
